\ \\ \LARGE\bf Speculative Evaluation in Particle Swarm Optimization \thanks{Matthew Gardner, Andrew McNabb, and Kevin Seppi are with the Department of Computer Science, Brigham Young University, 3361 TMCB, Provo, UT 84602 (phone: 801-422-8717; email: \{mjg82,a,k\}@cs.byu.edu).}

### 2010-04-08 honors_thesis/journal_paper/paper.tex
Fixed the line breaks in paper.tex after changing to the new bib style

Within the last few years, researchers have begun to recognize the need to
develop parallel implementations of PSO, publishing many papers on the subject.
The methods they have used include various synchronous algorithms
\cite{mcnabb-2007-parallel-pso-using-mapreduce,belal-2004-parallel-models-for-pso,chu-2006-intelligent-parallel-pso,jin-2005-pso-antenna-designs,parsopoulos-2004-parallel-vector-evaluated-pso,schutte-2004-parallel-global-optimization-with-pso}
and asynchronous algorithms
\cite{koh-2006-parallel-asynchronous-pso,mostaghim-2006-multi-objective-pso-on-grids,venter-2005-parallel-pso-asynchronous-evaluations}.  Parallelizing the
evaluation of the objective function can also be done in some cases, though
that is not an adaption of the PSO algorithm itself and thus is not the focus
of this paper.

>>>>

Within the last few years, researchers have begun to recognize the need to
develop parallel implementations of PSO, publishing many papers on the subject.
The methods they have used include various synchronous algorithms
\cite{mcnabb-2007-parallel-pso-using-mapreduce,
belal-2004-parallel-models-for-pso, chu-2006-intelligent-parallel-pso,
jin-2005-pso-antenna-designs, parsopoulos-2004-parallel-vector-evaluated-pso,
schutte-2004-parallel-global-optimization-with-pso} and asynchronous algorithms
\cite{koh-2006-parallel-asynchronous-pso,
mostaghim-2006-multi-objective-pso-on-grids,
venter-2005-parallel-pso-asynchronous-evaluations}.  Parallelizing the
evaluation of the objective function can also be done in some cases, though
that is not an adaption of the PSO algorithm itself and thus is not the focus
of this paper.
